---
title: "Reproducible Document"
author: "Christine Thoning"
format: html
  

---
Christine Thoning 
PhD Student 
SFS Group
SDU

# Introduction 
Here is the **introduction** to my *project*

# Methods and Results 
Methods and Results are a very **important** part of a *project*.
## Analysis
*Where* would we be without **analysis**?
# Discussion 
Discussion is where we *elevate* our **science!**

```{r}
2+2
```


Get some practice writing Markdown by completing these tasks in the doc/learning.qmd file.

Right under the YAML header, insert a list (either numbered or unnumbered) with your name and affiliation(s)/institution(s).
Create three level 1 headers (#), called “Intro”, “Methods and Results”, and “Discussion”.
Create a level 2 header (##) under “Methods and Results” called “Analysis”.
Write one random short sentence under each header. Bold (**word**) one word in each and italicize (*word*) another.
Insert a code chunk to make a simple calculation (e.g. 2 + 2).
Finally, add and commit these changes into the Git history with ⌃⌥M or with the Palette (⌘⇧P, then type “commit”).



# Setup 
```{r setup}
#| message: false
#| warning: false
library(tidyverse)
library(NHANES)
nhanes_small <- read_csv(here::here("data/NHANES_small.csv"))
```

```{r}
nhanes_small <- select(nhanes_small, age, sex, bmi, diabetes, phys_active, bp_sys_ave, bp_dia_ave, education)
nhanes_small
```

# Table of Results 

```{r}
nhanes_small %>%
  filter(!is.na(diabetes)) %>%
  group_by(diabetes, education) %>%
  summarise(
    mean_age = mean(age, na.rm = TRUE),
    mean_bmi = mean(bmi, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  knitr::kable(caption = "Mean Values of Age & BMI for each education and diabetes status")
```

# Prettier Table 

```{r}
#| echo = false
nhanes_small %>%
  filter(!is.na(diabetes), !is.na(education)) %>%
  group_by(diabetes, education) %>%
  summarise(
    mean_age = mean(age, na.rm = TRUE),
    mean_bmi = mean(bmi, na.rm = TRUE)
  ) %>%
  ungroup() %>%
  mutate(
    # Task 2a.
    mean_age = round(mean_age, 1),
    mean_bmi = round(mean_bmi, 1),
    # Task 2b.
    education = str_to_sentence(education)
  ) %>%
  rename(
    # Task 3.
    "Diabetes Status" = diabetes,
    "Education" = education,
    "Mean Age" = mean_age,
    "Mean BMI" = mean_bmi
  ) %>%
  knitr::kable(caption = "Mean values of Age and BMI for each education and diabetes status.")
```

```{r}

```



